---
output:
  word_document: default
  html_document: default
---


Twitter Data Collection using the developer account for my personal twitter, @larri_mill

``` {r}
library(rtweet)

mytoken <- create_token(
  app = "larri",
  consumer_key = "lLPUVichPD2C1wTQO5J1jlvx6",
  consumer_secret = "NYGgcf21R0MdBLAC0N0J9dlMxH0GibMcczpiWTc11zg1QniRRB",
  access_token = "4816226435-KBbDUtCsCxkugtyLOi1Vzfp0VqYAAKJ9HU3YlqX",
  access_secret = "5vKgKLrhZ5Apok5t3eUwwyyXhjLu96l8xrWpmDtt2BEgC")

``` 

Collecting n=1000 tweets with #sharpiegate. Saving in rda format. 1:45 PM 11/17/2020. 10,174 tweets collected.
``` {r}
tweets_sharpie <- search_tweets("sharpiegate", include_retweets = TRUE, n = 1000, retryonratelimit = TRUE,  token = mytoken)

save(tweets_sharpie, file="tweets_sharpie.rda")
```



Sharpie Gate Network Analysis
```{r}
tweets_sharpie <- read.csv("tweets.csv")
tweets <- subset(tweets_sharpie, is_retweet == "TRUE")

library(devtools) 
devtools::install_github("JohnCoene/twinetverse")
library(graphTweets)
library(twinetverse)

extractrt <- function(tweets_stopthesteal){
  rt <- tweets_stopthesteal %>% 
    gt_edges(screen_name, retweet_screen_name) %>% # get edges
    gt_nodes() %>% # get nodes
    gt_collect() # collect
  
  return(rt)
}

rtnet <- extractrt(tweets)

extractmt <- function(tweets){
  
  mt <- tweets %>% 
    gt_edges(screen_name, mentions_screen_name) %>% # get edges
    gt_nodes() %>% # get nodes
    gt_collect() # collect
  
  return(mt)
}

mtnet <- extractmt(tweets)

#define a function called nodes to extract node information from a network object

nodes <- function(net){
  
  c(edges, nodes) %<-% net
  nodes$id <- as.factor(nodes$nodes) 
  nodes$size <- nodes$n 
  nodes <- nodes2sg(nodes)
  nodes <- nodes[,2:5]
  
  return(nodes)
}

#define a function called edges to extract edge information from a network object

edges <- function(net){
  
  c(edges, nodes) %<-% net
  edges$id <- seq(1, nrow(edges))
  edges <- edges2sg(edges)
  
  return(edges)
}

#apply the two self-defined functions
rtnet_nodes <- nodes(rtnet)
rtnet_edges <- edges(rtnet)

mtnet_nodes <- nodes(mtnet)
mtnet_edges <- edges(mtnet)
```

Converting to igraph
``` {r}
library(igraph)

# use rtnet_edges as the edgelist and rtnet_nodes as the node list. Set the network type as directed

rt <- graph_from_data_frame(d=rtnet_edges, vertices=rtnet_nodes, directed=T) 

# see edge weight by copying the values from the size column in rtnet_edges

rt <- set_edge_attr(rt, "weight", value= rtnet_edges$size)

# we do the same for the mention network

mt <- graph_from_data_frame(d=mtnet_edges, vertices=mtnet_nodes, directed=T) 
mt <- set_edge_attr(mt, "weight", value= mtnet_edges$size)
```

using pageRank algorithm by google to identify top influencers
```{r}
pr <- page_rank(rt, algo = c("prpack"))
pr <- sort(pr$vector,decreasing = TRUE)
pr[1:10] #show the top 10 users ranked by PageRank
```

Visualize network!  PageRank score for node size, cluster id for assigning color.
```{r}
library(igraph)
library(visNetwork)
library(scales)

pr <- page_rank(rt, algo = c("prpack"))
V(rt)$size <- pr$vector*1000 #set node size by PageRank scores.

wc <- cluster_walktrap(rt)
V(rt)$color <- membership(wc)

kcore <- coreness(rt, mode="all") 
twocore <- induced_subgraph(rt, kcore>=2)

visIgraph(twocore,idToLabel = TRUE,layout = "layout_nicely") %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) 


```